---
title: "Git Commands"
author: "Robert Cline"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}

library(here)
library(readxl)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE) 
```  


```{r library-source,  echo=FALSE}  

## Load libraries from script  

source(here("scripts", "libraries.R"), local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
``` 


```{r installed-packages, echo=FALSE, eval=FALSE} 

# Verify loaded packages  

installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```  


## This file should be in the *manuscripts* folder.  

## This file should be in the *manuscripts* folder.  

### OurCodingClub - git commands  
```{r}

git_commands <- read_excel(here("data", "git-commands.xlsx"))
# View(git_commands)
```

<br>

[Connect exisiting RStudio Project to git and GitHub](https://www.youtube.com/watch?v=bUoN85QvC10)  
* Pat Schloss in *Riffomonas Project* has a YouTube tutorial that demonstrates how to create a new git project for version control from within an RStudio Project.  
* 1:32 minutes:  Create local git repository  

<br>



```{r git-command-table, echo=FALSE}
git_commands %>% 
  gt::gt()
```
 
 <br>
 <br>
 <br>
 
### **Undo Changes** with *Checkout, Revert and Reset*  
[Click here to see Nathan Williams' YouTube tutorial *Becoming a Data Scientist* on YouTube](https://www.youtube.com/watch?v=UmE0uf5UMzA)^[Nathan Williams' YouTube Video #5 - Undo Changes (checkout, revert, reset)]  
<br> 

* git log --oneline  

* git checkout \<shah\>  
  - read only view  
  - git checkout master 
    - return to master 
* git revert 
  - to undo commits  
  - undo for only one commit; 
  - good reason to keep commits to single issues  
  
* git reset \<shah\>  
  - removes all commits at and ahead.
  - reset undoes changes but saves them in working directory.
  - reset can get it back by adding back to staging
  - leaves files in working directory, therefore, you can get the reset back  

* git add . 
  git commit -m "Undo Reset"  
  
* git reset \<shah\> --hard  
  previous commits are gone.  Not coming back.  
  
**[Git Tutorial: Fixing common mistakes and undoing Bad Commits](https://www.youtube.com/watch?v=FdZecVxzJbk)**

<br>  
<br>   

### Branching  
[Nathan Williams video tutorial on Branching](https://www.youtube.com/watch?v=wVM4tfKsXBY&list=PLGPGLQRuosDKw42JcQvOU5qArkUb8kCDc&index=7)  
*Nathan Williams' tutorial #6 was very helpful in troubleshooting and deleting a new branch I created*^[Nathan Williams YouTube Video #6 - Branches]  

Create branch  
* git branch 
  - to tell which branch you are on
  
* git branch blog
  - creates a new branch 
  
* git checkout blog  
  - switches to new branch 
  
[Remove Branches](https://www.techiediaries.com/delete-local-remote-git-branches/#)^[How to remove local/remote Git Branches by Techiediearies] 
  
* git branch -D newbranch  
  - *capital -D deletes regardless of merge status*  
  - *deletes the local branch.*  Then push:  
  - *git push --delete origin branch-name*   
    - *deletes branch from remote*
<<<<<<< Updated upstream

### [Branch Tutorial by Alessandro Castellani](https://www.youtube.com/watch?v=pDmYNK68IEc)

=======
   

### [Branch Tutorial by Alessandro Castellani](https://www.youtube.com/watch?v=pDmYNK68IEc)

>>>>>>> Stashed changes
* git branch --list  
* git checkout newdocs  
* bit branch  
  - to check which branch we are on.
* git touch style.css  
  - to create a new file *style.css*  
<<<<<<< Updated upstream
=======
  
### [Working with *git stash* by Ihatetomatoes](https://www.youtube.com/watch?v=-aPoRU5W8lA)
<br>  
* git stash 
* **git stash -u**  
  - the dash u stashes untracted changes  
* git stash list  
* git stash show 0 
* git stash show -p 0 
  - -p shows branches  
  shashes are indexed 
* **git stash apply 0**  (the index of the stash we want to bring back)  
* Save stash with a custom message:  
  - **git stash push -m "Updated text."**    
  - git stash list 
>>>>>>> Stashed changes
  
### [Working with *git stash* by Ihatetomatoes](https://www.youtube.com/watch?v=-aPoRU5W8lA)
<br>  
* git stash 
* **git stash -u**  
  - the dash u stashes untracted changes  
* git stash list  
* git stash show 0 
* git stash show -p 0 
  - -p shows branches  
  shashes are indexed 
* **git stash apply 0**  (the index of the stash we want to bring back)  
* Save stash with a custom message:  
  - **git stash push -m "Updated text."**    
  - git stash list 
  

### Create a new brach for the stash  
* git stash branch new-branch 0 

<<<<<<< Updated upstream
=======
### Create a new brach for the stash  
* git stash branch new-branch 0 

>>>>>>> Stashed changes
### Bring back changes not staged for commit   
* git stash pop  
  - takes the last stash you put in, and apply to working directory  
* **git stash clear**  
  - removes the list of all stashes.  
  


