---
title: "Git Commands"
author: "Robert Cline"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) 

library(gt)
library(tidyverse)
library(here)
```

### OurCodingClub - git commands  
```{r}
library(readxl)
git_commands <- read_excel(here("data", "git-commands.xlsx"))
# View(git_commands)
```

```{r git-command-table, echo=FALSE}
git_commands %>% 
  gt()
```
 
 <br>
 <br>
 <br>
 
### **Undo Changes** with *Checkout, Revert and Reset*  
[Click here to see Nathan Williams' YouTube tutorial *Becoming a Data Scientist* on YouTube](https://www.youtube.com/watch?v=UmE0uf5UMzA)  
<br> 

* git log --oneline  

* git checkout \<shah\>  
  - read only view  
  - git checkout master 
    - return to master 
* git revert 
  - to undo commits  
  - undo for only one commit; 
  - good reason to keep commits to single issues  
  
* git reset \<shah\>  
  - removes all commits at and ahead.
  - reset undoes changes but saves them in working directory.
  - reset can get it back by adding back to staging
  - leaves files in working directory, therefore, you can get the reset back  

* git add . 
  git commit -m "Undo Reset"  
  
* git reset \<shah\> --hard  
  previous commits are gone.  Not coming back.  
  
### [Git Tutorial: Fixing common mistakes and undoing Bad Commits](https://www.youtube.com/watch?v=FdZecVxzJbk)  

<br>  
<br>   

### [Nathan Williams on Branching](https://www.youtube.com/watch?v=wVM4tfKsXBY&list=PLGPGLQRuosDKw42JcQvOU5qArkUb8kCDc&index=7)  




  



